Bow shocks, bow waves, and dust waves

### 2018-11-07 papers/Papers1234/sec-dust-case-studies.tex
Start on graph for Sickle Nebula in Carina
Add some figures to the observations section

\section{Observational evidence for radiation-supported bows}
\label{sec:case-studies}

@@

@@

\(\theta^1\)\,Ori~D (Ney--Allen nebula) \citep{Robberto:2005a}

@@

>>>>

\section{Observational case studies}
\label{sec:case-studies}

@@

\subsection{Evidence for radiation-supported bows}

@@

\newcommand{\thD}{\(\theta^1\)\,Ori~D}
\th1D{} (Ney--Allen nebula) \citep{Robberto:2005a}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/orion-LP-and-th1D-color}
  \caption{Bows driven by the OB stars \thD{} and LP~Ori in the Orion
    Nebula.  (a)~Large-scale infrared view of the Orion Molecular
    Cloud.  Red, green, and blue intensity show respectively Herschel
    PACS observations at \SIlist{160; 70}{\um}, and Spitzer IRAC
    observations at \SI{8}{\um}.  Red traces thermal emission from
    cool dust (\(T < \SI{30}{K}\)) in the dense molecular filament.
    Green traces thermal emission from warmer dust
    (\(T \approx \SI{40}{K}\)) in the neutral PDR, which is heated by
    far-ultraviolet radiation from the OB stars in the cluster. Blue
    traces emission from PAH \SIlist{7.6;7.85}{\um} bands in the same
    neutral PDR plus thermal emission from hotter dust
    (\(T > \SI{100}{K}\)), which is found inside the ionized \hii{}
    region.  (b)~Zoom on the central parsec of the Orion Nebula (M42),
    showing short-wavelength mid-infrared emission from Spitzer IRAC
    observations (\SIlist{8.0;5.8;4.5}{\um}).  Red shows the same as
    blue in panel~a.  Green show predominantly the \SI{6.2}{\um} PAH
    band.  Blue shows mainly stellar photospheric emission, plus a
    minor contribution due to the Br~\(\alpha\) emission line from ionized
    gas. Some major components of the nebula are labelled: the
    Trapezium cluster, which contains the majority of the massive
    stars; the Kleinmann-Low reflection nebula, illuminated by massive
    stars embedded in the molecular filament; the Orion Bar, a
    prominent edge-on ionization front and PDR.  (c)~Zoom on the
    central \SI{0.1}{pc} of the Trapezium cluster, showing longer
    wavelength mid-infrared emission from UKIRT MAX
    (\SIlist{19.7;10.1}{\um}).  In this central zone, these
    wavelengths (shown in red and green) are dominated by warm
    (\SIrange{100}{300}{K}) silicate grains, while the IRAC
    \SI{5.8}{\um} emission (blue) shows stellar photospheres and the
    very warmest dust.}
  \label{fig:orion-bows}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/ney-allen-sed}
  \caption{Infrared spectral energy distribution of the Ney--Allen
    nebula that surrounds \thD. }
  \label{fig:ney-allen-sed}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/lp-ori-sed}
  \caption{Optical/infrared spectral energy distribution of the LP Ori
    and associated nebula. }
  \label{fig:lp-ori-sed}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/lp-ori-wfpc2-continuum-subtract}
  \caption{Narrow-band images of LP Ori nebula }
  \label{fig:lp-ori-sed}
\end{figure}
